%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5.245pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Timothy Zheng} \\ \vspace{2pt}
    \small Computer Science and Finance \\
    \small Toronto, ON $|$ 
    \href{mailto:timothy.zheng@uwaterloo.ca}{\underline{timothy.zheng@uwaterloo.ca}} $|$ 
    \small Cell available on request
    \\ \vspace{2pt}
    \href{https://timothyzheng.com}{\underline{timothyzheng.com}} $| $
    \href{https://linkedin.com/in/timothyzheng}{\underline{linkedin.com/in/timothyzheng}} $|$
    \href{https://github.com/Ti1mmy}{\underline{github.com/Ti1mmy}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{2021 - Present}
      {Candidate for Bachelor of Computing and Financial
Management}{Waterloo, ON}
          \resumeItemListStart
            \resumeItem{Dean's List.}
            \resumeItem{Relevant Coursework: Financial Data Analysis, Functional Programming, Algorithm Design \& Data Abstraction.}
            \resumeItem{Clubs and Activities: UW Badminton Club Executive, UW Formula Motorsports Business Section.}

            
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Skills Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, HTML/CSS, SQL, Markdown, LaTeX.} \\
     \textbf{Technical Skills}{: CI/CD, Web Scraping, SSH/Linux Shell, Microsoft Office Suite (Excel, Word, Outlook).} \\
     \textbf{Libraries}{: Pandas, Matplotlib, yFinance, Flask, React, Bootstrap, BeautifulSoup4, Google Cloud Platform.} \\
     \textbf{Tools/Applications}{: Azure Static Web Apps, Heroku, Git, VS Code, Jupyter Notebook, PuTTY, Ubuntu, GNU Bash.}
    }}
 \end{itemize}

%-----------Work EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IMOxKids2AI}{Jun – Oct 2021}
      {Python Instructor}{Remote}
      \resumeItemListStart
        \resumeItem{Instructed a class of six students from Dublin, Ireland virtually using Zoom, teaching intermediate programming concepts (\textbf{functions, data structures, recursion, search and sorting algorithms}) over a \textbf{five month} term.}
        \resumeItem{Engaged with students and parents with weekly personalized progress reports and presented live visualizations of sort and search algorithms using playing cards, resulting in an end-of-term class average of \textbf{94.6\%}.}
      \resumeItemListEnd
     
    \resumeSubHeadingListEnd

%-----------COMMUNITY AND LEADERSHIP-----------
\section{Community \& Leadership}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Director of Operations}{Oct 2020 – Jun 2021}
      {St. Robert Coding Club}{Thornhill, ON}
      \resumeItemListStart
        \resumeItem{Directed, instructed and managed a \textbf{150-member} club of high school students interested in coding.}
        \resumeItem{Prepared students for the CEMC Canadian Computing Competition in the Junior and Senior stages.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://gist.github.com/Ti1mmy/03a35f7816a1a3ba7c00df52d2bf80d0}{\underline{Smart Stock Portfolio Generator}}} $|$ 
          \emph{Jupyter Notebook, Pandas, Matplotlib, NumPy, yFinance}}{Oct -- Dec 2021}
          \resumeItemListStart
            \resumeItem{Led the creation of a dynamic finance program in \textbf{Python} with 2 classmates that quantitatively analyzed live financial data to produce the most volatile portfolio from an arbitrary list of stock tickers.}
            \resumeItem{Calculated beta coefficients, standard deviation, Sharpe ratio, and stock option interest ratios using \textbf{Pandas} and \textbf{NumPy} to rank stocks and used \textbf{Monte} \textbf{Carlo} methods to determine optimal portfolio weight combinations.}
            \resumeItem{Presented statistical findings by writing code in a \textbf{Jupyter Notebook}, accompanied with commentary written in \textbf{Markdown} and \textbf{LaTeX} and graphs generated using \textbf{Matplotlib}.}
            \resumeItem{Optimized code execution by threading and caching API calls to our financial data source, yielding a \textbf{20x} \textbf{decrease} in run time and achieving the highest class grade of \textbf{97.5\%} and \href{https://uwaterloo.ca/school-of-accounting-and-finance/news/congratulations-teams-won-cfm-101-team-competition}{\underline{2nd place}} in a real-world simulation competition.}
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd
    
    
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/DisCardApp/DisCard}{\underline{DiscardApp}}} $|$ 
          \emph{JavaScript, HTML, Google Firebase, BeautifulSoup4, Google Places API, Azure CI/CD}}{Jun 2021}
          \resumeItemListStart
            \resumeItem{AtlasHacks II First Place Winner, byteKode Summer 2021 Runner-up.}
            \resumeItem{Created a web application in a team of 4 to display the best credit card to use in your wallet, stored on \textbf{Google Firebase}, by determining where you are shopping using \textbf{Google Places} categories, \textbf{web-scraped} Rakuten referral links using \textbf{BeautifulSoup4} and a curated Canadian credit card list attracting \textbf{800 unique visitors/mo}.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
    
          
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/Ti1mmy/CheckinWithme}{\underline{CheckinWithMe}}} $|$ 
          \emph{Python, Natural Language Processing, AstraDB, Discord.py, Heroku CI/CD}}{May 2021}
          \resumeItemListStart
            \resumeItem{Mental Health Hacks Hackathon Winner: Best use of Linode Cloud, Best Domain Name from Domain.com.}
            \resumeItem{Led a team of 4 to create and deploy a Discord bot in Python with \textbf{Heroku} that uses \textbf{tone/sentiment analysis} to detect and respond to users' moods, generating weekly personalized mood reports using data stored on \textbf{AstraDB} leading to an increased awareness about their mental health.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
    
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/STR-Coding-Club/RobCoin}{\underline{RobCoin}}} $|$ 
          \emph{Python, Flask, OpenSSL}}{Apr 2021 -- Jun 2021}
          \resumeItemListStart
            \resumeItem{Co-created original Python code and instructional material for a \textbf{proof of work cryptocurrency} networked with Flask and OpenSSL from scratch.}
            \resumeItem{Tailored original instructional material alongside code development to educate Coding Club members in \textbf{blockchain, public/private-key cryptography, hash functions} and \textbf{distributed computing}. }
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
